Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2020-12-29 GWLDCII.tex
a few last things

Wilson loop diagrams, as we will study them, are objects given by a perturbative expansion of the holomorphic Wilson loop in twistor space.
Classically, the interactions of the theory were studied as maximal helicity violating diagrams ($MHV$ diagrams), next-to-maximal helicity violating diagrams and so on ($N^kMHV$ diagrams) in momentum space. Adamo and Mason, in \cite{Adamo:2011pr}, gave an elegant formulation for the $N^kMHV$ diagrams in twistor space. The Wilson loop diagram perspective of this paper is dual to this twistor representation of $MHV$ diagrams.
The objects are closely related and carry the same information.  We choose to emphasize the dual perspective by our focus on the Wilson loop diagrams.

@@

On both of the last two points, we differ from the standard convention in the physics literature, where propagators are written as ordered pairs $(i,j)$ with $1 \leq i<j \leq n$.  Additionally, note that in this paper, we allow for the propagator set $\cP$ to be empty. This is for mathematical convenience, even though these diagrams do not correspond to tree level scattering amplitudes.  Additionally, since $\cP$ is defined to be a set of pairs, parallel propagators are already excluded from this formulation, but nothing of physical importance is lost as the admissibility restriction, Definition~\ref{admisdfn}, would have excluded them on physical grounds.

@@

The flavour of the calculations is similar to\footnote{Thanks to a referee for pointing this paper out.} \cite{CGdyck} as in both our paper and theirs the bijections are very explicit with a similar iterative flavour using Le diagrams and Grassmann necklaces related to another class of objects, for us Wilson loop diagrams and for them unit interval orders.  For them, as us, the Le diagrams are particularly useful for understanding the dimensions of positroid cells since the dimension becomes the count of the number of plusses.  The ubiquitous Catalan numbers arise for them, as for us in \cite{generalcombinatoricsI}.  The specific subclasses of positroids we work with are, however, different.  This basic methodology of gaining insight from bijections is very common in combinatorics.

@@

In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation). Note that this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary. Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}). The diagram $V$ is guaranteed to be admissible, since it was formed by removing a propagator from a diagram that was at least weakly admissible. \todo{Make certain we don't start sentences with simbols}

@@

Note that the positroid cells associated to the Amplituhedron are of dimension $4|\cP|$. In \cite[section 2]{non-orientable}, Agarwala and Marcott associated a Deodhar component\footnote{Since Deodhar components play no role in this paper, the interested reader is referred to \cite{non-orientable} for more details on this.} to each Wilson loop diagram, and showed that the dimension of this Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
%\[|\cP| + \text{ the dimension of associated positroid cell}.\]
Combining this with Theorem~\ref{thm dim}, we see that the Deodhar component associated to a Wilson loop diagram is $4|\cP|$-dimensional, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron. It is worth noting that the Amplituhedon is defined by a projection of a set of $4|\cP|$ dimensional positroid cells, while the $4|\cP|$-dimensional cells of the Wilson loop diagram lie in $\mathbb{G}_\R$.
While it is conjectured that the geometry of the Amplituhedron is related to the geometry of the Wilson loop diagrams, in part due to their common physical origin, the $3 |\cP|$ dimensional positroid cells defined by the Wilson loop diagrams do not seem to bear any geometric relationship to the $4|\cP|$ dimensional cells parametrized by the Amplituhedron.
%To  date, there is no evidence to suggest that the $3|\cP|$ dimensional positive cells of $\Gr(|\cP|, n)$ defining the Wilson loop diagrams are related to the $4|\cP|$ dimensional positive cells defining the Amplituhedron.  \sanote{This para adresses point 3 of report Y. Should there be a similar paragraph in the intro? Should it be moved?} \sanote{futzed some  more}

>>>>

Wilson loop diagrams, as we will study them, are objects given by a perturbative expansion of the holomorphic Wilson loop in twistor space.
Classically, the interactions of the theory were studied as maximal helicity violating diagrams ($MHV$ diagrams), next-to-maximal helicity violating diagrams and so on ($N^kMHV$ diagrams) in momentum space. Adamo and Mason, in \cite{Adamo:2011pr}, gave an elegant formulation for the $N^kMHV$ diagrams in twistor space. The Wilson loop diagram perspective of this paper is dual to this twistor representation of $N^kMHV$ diagrams.
The objects are closely related and carry the same information.  We choose to emphasize the dual perspective by our focus on the Wilson loop diagrams.

@@

On both of the last two points, we differ from the standard convention in the physics literature, where propagators are written as ordered pairs $(i,j)$ with $1 \leq i<j \leq n$.  Additionally, note that in this paper, we allow for the propagator set $\cP$ to be empty. This is for mathematical convenience, even though these diagrams do not correspond to tree level scattering amplitudes.  Additionally, since $\cP$ is defined to be a set of pairs, parallel propagators (propagators starting and ending on the same pair of edges) are already excluded from this formulation, but nothing of physical importance is lost as the admissibility restriction, Definition~\ref{admisdfn}, would have excluded them on physical grounds.

@@

The flavour of the calculations is similar to \cite{CGdyck} as in both our paper and theirs\footnote{Thanks to a referee for pointing this paper out.} the bijections are very explicit with a similar iterative flavour using Le diagrams and Grassmann necklaces related to another class of objects, for us Wilson loop diagrams and for them unit interval orders.  For them, as us, the Le diagrams are particularly useful for understanding the dimensions of positroid cells since the dimension becomes the count of the number of plusses.  The ubiquitous Catalan numbers arise for them, as for us in \cite{generalcombinatoricsI}.  The specific subclasses of positroids we work with are, however, different.  This basic methodology of gaining insight from bijections is very common in combinatorics.

@@

In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation). Note that this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary. Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}). The diagram $V$ is guaranteed to be admissible, since it was formed by removing a propagator from a diagram that was at least weakly admissible.

@@

Note that the positroid cells associated to the Amplituhedron are of dimension $4|\cP|$. In \cite[section 2]{non-orientable}, Agarwala and Marcott associated a Deodhar component\footnote{Since Deodhar components play no role in this paper, the interested reader is referred to \cite{non-orientable} for more details on this.} to each Wilson loop diagram, and showed that the dimension of this Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
%\[|\cP| + \text{ the dimension of associated positroid cell}.\]
Combining this with Theorem~\ref{thm dim}, we see that the Deodhar component associated to a Wilson loop diagram is $4|\cP|$-dimensional, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron. It is worth noting that the Amplituhedon is defined by a projection of a set of $4|\cP|$ dimensional positroid cells, while the $3|\cP|$-dimensional cells of the Wilson loop diagram lie in $\mathbb{G}_\R$.
While it is conjectured that the geometry of the Amplituhedron is related to the geometry of the Wilson loop diagrams, in part due to their common physical origin, the $3 |\cP|$ dimensional positroid cells defined by the Wilson loop diagrams do not seem to bear any geometric relationship to the $4|\cP|$ dimensional cells parametrized by the Amplituhedron.
%To  date, there is no evidence to suggest that the $3|\cP|$ dimensional positive cells of $\Gr(|\cP|, n)$ defining the Wilson loop diagrams are related to the $4|\cP|$ dimensional positive cells defining the Amplituhedron.  \sanote{This para adresses point 3 of report Y. Should there be a similar paragraph in the intro? Should it be moved?} \sanote{futzed some  more}
